\documentclass{article}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{courier}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\usepackage[top=.75in, bottom=.75in, left=.75in,right=.75in]{geometry}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{listings}
\lstset{basicstyle=\small\ttfamily}
\usepackage{mdframed}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{soul}
\usepackage{upquote}
\usepackage{xcolor}

% http://www.monperrus.net/martin/copy-pastable-ascii-characters-with-pdftex-pdflatex
\lstset{
upquote=true,
columns=fullflexible,
literate={*}{{\char42}}1
         {-}{{\char45}}1
         {^}{{\char94}}1
}
\lstset{
  moredelim=**[is][\color{blue}\bf\small\ttfamily]{@}{@},
}

% http://tex.stackexchange.com/questions/40863/parskip-inserts-extra-space-after-floats-and-listings
\lstset{aboveskip=6pt plus 2pt minus 2pt, belowskip=-4pt plus 2pt minus 2pt}

\usepackage[colorlinks,urlcolor={blue}]{hyperref}

\begin{document}

\fancyfoot[L]{\color{gray} C4CS -- F'16}
\fancyfoot[R]{\color{gray} Revision 1.0}
\fancyfoot[C]{\color{gray} \thepage~/~\pageref*{LastPage}}
\pagestyle{fancyplain}


\title{\textbf{Advanced Homework 11}}
\author{\textbf{\color{red}{Due: Saturday, December 3, 10:00PM (Hard Deadline)}}}
\date{}
\maketitle


\section*{Submission Instructions}
To receive credit for this assignment you will need to stop by someone's
office hours and demo your new skills.

\section*{Taking IDEs Farther}
In lecture we showed valgrind running in Xcode, we looked at online (text-
based) IDEs, we saw IDEs that didn't even include a ``text editor.'' Your task
is to push your IDE usage beyond what was done in the regular homework. Try
2 new things, and be ready to demo them to a course staff member.

\begin{enumerate}
\item Create an account with an online IDE service. Migrate a project there,
      and be sure to use source control (GitHub or GitLab). Do some non-trivial
      development, like finishing your current class project for another class,
      or making meaningful commits (locally) to a class or personal project.
\item Build an app with 2+ hours of development time in a ``Visual IDE'' like
      Scratch or App Inventor.
\item Set up 4 or 5 IFTTT recipes (the more related they are, the better).
\item Trick out your desktop IDE (Xcode or Visual Studio) to extend or swap out
      current functionality. This would be like using g++ in the IDE, or make,
      or valgrind, gcov, eslint, etc.
\end{enumerate}

\emph{You are welcome to do this assignment either on your native operating
  system on your machine or inside the class VM, whichever helps you learn the
  most.}

\end{document}
