\documentclass{article}
\usepackage[T1]{fontenc}

\usepackage{amssymb}
\usepackage{courier}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage[top=.75in, bottom=.75in, left=.75in,right=.75in]{geometry}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{listings}
\lstset{basicstyle=\small\ttfamily}
\usepackage{mdframed}
\usepackage{parskip}
\usepackage{soul}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{upquote}
\usepackage{xcolor}

% http://www.monperrus.net/martin/copy-pastable-ascii-characters-with-pdftex-pdflatex
\lstset{
upquote=true,
columns=fullflexible,
keepspaces=true,
literate={*}{{\char42}}1
         {-}{{\char45}}1
         {^}{{\char94}}1
}
\lstset{
  moredelim=**[is][\color{blue}\bf\small\ttfamily]{@}{@},
}

% http://tex.stackexchange.com/questions/40863/parskip-inserts-extra-space-after-floats-and-listings
\lstset{aboveskip=6pt plus 2pt minus 2pt, belowskip=-4pt plus 2pt minus 2pt}



\usepackage[colorlinks,urlcolor={blue}]{hyperref}
\usepackage[capitalise,nameinlink,noabbrev]{cleveref}
\crefname{section}{Question}{Questions}
\Crefname{section}{Question}{Questions}

\begin{document}

%\fancyhead[C]{\hl{Select the right page in Gradescope or we will not grade the question!}}
%\fancyhead[L]{}
%\fancyhead[R]{}

\fancyfoot[L]{\color{gray} C4CS -- W'16}
\fancyfoot[R]{\color{gray} Revision 1.0}
\fancyfoot[C]{\color{gray} \thepage~/~\pageref*{LastPage}}
\pagestyle{fancyplain}



\title{\textbf{Homework 12\\Towards a Development Environment}}
\author{Assigned: Friday, April 1}
\date{\textbf{\color{red}{Due: Friday, April 8, 11:00AM (Hard Deadline)}}}
\maketitle


\section*{Submission Instructions}
Submit a pointer to your dotfiles repository
\href{https://docs.google.com/a/umich.edu/forms/d/1ruvqtb7yh5SLkPJf6DHSEvIe7XDxuxgRqiH15aS5guQ/viewform}{here}.

\section{A dotfiles repository}

As we've seen in class, many tools store their configuration in ``dotfiles''
in your home directory. While this is convenient for configuring things on one
machine, often you may have multiple machines that you use (desktop at
work, laptop for travel, etc). It would be really nice if all of these things
stayed in sync.

Fortunately, we've also learned a great tool for keeping things synchronized
in this class -- git! Keeping your configuration files in git has the added
benefit that you can try changes that your aren't sure if you will like
(e.g\ trying out \href{http://blog.sanctum.geek.nz/vi-mode-in-bash/}{vi mode
in bash}) knowing that you can easily revert them later.

The trick is that it's not a good idea to make your home directory a git
repository (because then every file in your home directory would be in that
repository!). Instead, create a folder named \texttt{dotfiles}, make that a
repository, and then use symlinks to point from where tools expect your
dotfiles (in your home directory) to where they actually are (the dotfiles
folder):

\begin{lstlisting}
  $ ls -l ~/.bashrc
  lrwxr-xr-x  1 ppannuto  staff  40 Mar 31 23:43 /Users/ppannuto/.bashrc ->
  /Users/ppannuto/Dropbox/dotfiles/.bashrc
\end{lstlisting}


\subsection*{The Assignment}
Create a dotfiles repository. Move your existing \texttt{.bashrc} file into
this repository, commit it, and set up a symlink from your home directory for
bashrc. Pick at least one other dotfile to move under version control and add
it to this repository. For ideas, here are the files in my dotfiles folder:

\begin{lstlisting}[escapechar=!]
  .bash_aliases .bash_profile .bashfuncs .bashrc .gitconfig .gitignore .gsdesktop-helper!\footnote{Pour one out... (dead config file from \href{https://github.com/intarstudents/GSDesktop-Helper}{this} for \href{https://en.wikipedia.org/wiki/Grooveshark}{Grooveshark})}!
  .hgrc .inputrc .pypirc .screenrc .vim!\footnote{This is actually a directory for \href{https://github.com/tpope/vim-pathogen}{Pathogen}}!  .vimrc
  setup_dotfiles.sh!\footnote{This is a script that deletes any existing dotfiles (e.g.\ things usually ship with a template \texttt{.bashrc}) and replaces them with symlinks to the dotfile repo. It also handles ssh-config, which lives at \textasciitilde/.ssh/config}!
  ssh-config
\end{lstlisting}

You can also find \emph{lots} of other dotfiles repositories on the web with
tons of cool ideas for configurations. Some of the staff even have pretty good
dotfiles repositories\dots

Use any repository hosting service (Umich Gitlab, GitHub, personal server, etc)
to make your dotfiles repo publically accessible. Then submit a link to your
repository \href{https://docs.google.com/a/umich.edu/forms/d/1ruvqtb7yh5SLkPJf6DHSEvIe7XDxuxgRqiH15aS5guQ/viewform}{here}.

\section{The Practice Exam}

Did you do the practice exam? You should probably do the practice exam.
Homework this week is super short so that you have more time to do the
practice exam.

(No. You do not have to turn anything in for this ``question''.)


\end{document}
