\documentclass{article}
\usepackage[T1]{fontenc}

\usepackage{amssymb}
\usepackage{courier}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage[top=.75in, bottom=.75in, left=.75in,right=.75in]{geometry}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{listings}
\lstset{basicstyle=\small\ttfamily}
\usepackage{mdframed}
\usepackage{parskip}
\usepackage{soul}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{upquote}
\usepackage{xcolor}

% http://www.monperrus.net/martin/copy-pastable-ascii-characters-with-pdftex-pdflatex
\lstset{
upquote=true,
columns=fullflexible,
keepspaces=true,
literate={*}{{\char42}}1
         {-}{{\char45}}1
         {^}{{\char94}}1
}
\lstset{
  moredelim=**[is][\color{blue}\bf\small\ttfamily]{@}{@},
}

% http://tex.stackexchange.com/questions/40863/parskip-inserts-extra-space-after-floats-and-listings
\lstset{aboveskip=6pt plus 2pt minus 2pt, belowskip=-4pt plus 2pt minus 2pt}

\usepackage[colorlinks,urlcolor={blue}]{hyperref}
\usepackage[capitalise,nameinlink,noabbrev]{cleveref}
\crefname{section}{Question}{Questions}
\Crefname{section}{Question}{Questions}

\begin{document}


%%% TITLE INFO INSERTED HERE AUTOMATICALLY


\section*{\emph{Optional} Readings}

{\small

\subsection*{Interrupting Developers and Makers vs Managers}
In lecture we spent a little time talking about the mental model of
programmers. As computer science grows, there is a growing body of research
and wisdom in how to maximize the efficacy of individual programmers.
One of the key revelations is that programming is a creative process. It
requires time to ``page in'' what you are working on. As a result, even small
interruptions (read: text messages) can be far more costly than you may
realize.

\medskip
\noindent
\url{http://thetomorrowlab.com/2015/01/why-developers-hate-being-interrupted/}\\
\emph{Why developers hate being interrupted}, by Derek Johnson at The Tomorrow Lab.

\noindent
\url{http://www.paulgraham.com/makersschedule.html}\\
\emph{Maker's Schedule, Manager's Schedule}, by Paul Graham, co-founder of Y~Combinator.

\medskip
\noindent
Once you are in a job environment and meetings become a regular thing, one of
the best tricks I learned is to schedule a few 4-hour meetings with yourself
throughout the week. It both prevents others from interrupting you (your
calendar shows you as busy) and lets you mentally prepare for a good, reliable
work session.
(A similar alternative, some find
\href{http://lifehacker.com/productivity-101-a-primer-to-the-pomodoro-technique-1598992730}{pomodoro}
helpful)

%As you work on homework this week, especially for your programming-heavy EECS
%classes, I encourage you to try turning off your phone (yes, seriously, off),
%close your browser and start from a blank session (hiding the browser window
%with your Facebook tab doesn't help if messenger keeps dinging), and see if
%your software development experience is any different.\footnote{
%  It can be hard to be not keep opening a Facebook tab every time you Google
%  something. Sometimes when I am having a particularly hard time forcing
%  myself to work, I'll ``black hole'' things I might be tempted to distract
%  myself with: \\
%  \texttt{printf "\# Disable some sites\char`\\n127.0.0.1\char`\\tfacebook.com\char`\\n127.0.0.1\char`\\treddit.com\char`\\n" | sudo tee -a /etc/hosts}\\
%  You can undo this by editing \texttt{/etc/hosts} later.
%}

\subsection*{Software Engineering in the Real World}
\url{http://blogs.msdn.com/b/peterhal/archive/2006/01/04/509302.aspx}\\
\emph{What Do Programmers Really Do Anyway?}, by Peter Hallam, then-Microsoft~Developer
\begin{quote}
  \emph{%
    Why is 5 times more time spent modifying code than writing new code? The
    answer is that new code becomes old code almost instantly.  Write some new
    code. Go for coffee. All of sudden you've got old code.
  }
\end{quote}
This post gives a nice perspective on what enterprise software engineering is
really like. School projects are misleading. Rarely in life will you be faced
with a spec and a blank text file. Far more often you are building on or
improving something that came before you and will exist long after you.

\medskip
\noindent
\url{http://www.joelonsoftware.com/articles/fog0000000069.html}\\
\emph{Things You Should Never Do, Part I}, by Joel Spolsky
\begin{quote}
  \emph{It's harder to read code than to write it.}
\end{quote}
Building on the previous, rarely in life are you handed a spec and a blank text
file, often in life you are handed a spec and a pile of (seemingly) spaghetti
code that does at least some of it. This article discusses the hidden value of
the built-up institutional knowledge and the high value of working code.

\medskip
\noindent
\emph{When was the last time you saw a hunt-and-peck pianist?} -Jeff Atwood,
co-founder of Stack Overflow and Discourse.\\
Some extras on the
\href{http://blog.codinghorror.com/we-are-typists-first-programmers-second/}
{value of being a good typist}
and
\href{http://blog.codinghorror.com/going-commando-put-down-the-mouse/}
{ditching the mouse for the keyboard}.

}

% I had some intention of some articles on text editors here, but I think these
% are actually more useful, if a bit preachy


\newpage
\section{Trying out some of the fancy features}

People often complain about how difficult the simple things are using
text-based text editors. Indeed, Notepad (or TextEdit) make changing some
text and saving a file very easy.
In this question we explore some of the things that Notepad (and nano, and
gedit, and Microsoft Word\dots) cannot do.

I encourage you to play around with things as you work through this question.
The intent is to expose you to features you may not have been aware of along
with some context for why they are useful.

There are many things to try here.
\textbf{For credit on this question, you only need to choose any 5.}
That said, I encourage you to try all of these.

For this question, you may choose \texttt{vim} or \texttt{Emacs}, whichever
you are more comfortable with.

\bigskip
\hrule
To start, grab copies of two files full of code:
\begin{quote}
  \texttt{\# Examples from \url{http://web.mst.edu/~price/cs53/code_example.html}}\\
  \texttt{wget \url{http://web.mst.edu/~price/cs53/fs11/workDecider.cpp}}\\
  \texttt{wget \url{http://web.mst.edu/~price/cs53/KatsBadcode.cpp}}
\end{quote}
\smallskip
\hrule
\bigskip

\begin{enumerate}
  \item Sometimes you will come across some ugly code. Your editor can help
    make it better. Open \texttt{KatsBadcode.cpp}. Among other issues, the
    really bad tabbing makes this hard to read.\\
    \textbf{Describe how to automatically fix the indentation for the whole file.}
    \vspace{6em}
  \item Editing one file is nice, but often it's really useful to compare
    files side-by-side (source and headers, spec and implementation).\\
    \textbf{Describe the command sequence to create a window split (within your
        text editor) side-by-side with your current window, switch to it, and then open a file in that window.}\\
    \vspace{6em}

    Try playing around with these two views, copy/paste code between them,
    bind them so they scroll together, resize them, add more splits.\\
  \item Editors also have pretty nice integration with compilation tools. With
    \texttt{KatsBadcode.cpp} open, try typing \texttt{:make KatsBadcode} in
    \texttt{vim} or \texttt{M-x compile<enter>make KatsBadcode} in
    \texttt{Emacs}.\footnote{
      Descriptions of \texttt{Emacs} commands are usually written as
      \texttt{C-c} or \texttt{M-x}, which mean ``Ctrl+C'' or ``Meta+x''
      respectively. Meta is often mapped to the escape and/or alt key,
      \texttt{M-x} means press Escape and then x or hold alt and press x.
    }
    \begin{quote}
      First cool thing that happened: Yes, you can run \texttt{make}
      \emph{without} any Makefile anywhere. We'll cover how that happened
      during build-system week.
    \end{quote}
    Building \texttt{KatsBadcode.cpp} will fail with several errors.\\
    \textbf{Describe how to navigate between compilation errors automatically.}
    \vspace{6em}
  \item While C-style languages support \texttt{/* block comments */}, others
    such as Python have no block comments and require you to put a \texttt{\#}
    at the beginning of every line.\\
    \textbf{Describe how to efficiently comment out a large block of Python code.}
    \vspace{6em}
  \item (This one is actually about the terminal emulator): The normal
    keyboard shortcuts to copy/paste are Ctrl-C and Ctrl-V. These do not work
    in the terminal, however.\\
    \textbf{Explain what Ctrl-C does in a terminal.}\\
    ~\\
    ~\\
    ~\\
    ~\\
    ~\\
    \textbf{Describe how to copy/paste using the keyboard within the terminal (not
    in your text editor that may be running within terminal).}
    \vspace{6em}
  \item The default cut/copy/paste(/put/yank/kill) operations do not put text in
    the system clipboard (that is you cannot copy/paste into/from other
    applications).
    \textbf{Describe how to copy/paste a region of text to/from the system
    clipboard using your text editor.}
    \vspace{6em}
  \item Many times you have a repetitive task that you need to do say 10 or 20
    times. It's too short to justify writing a script or anything fancy, but
    it's annoying to type the same thing over and over again. As example,
    reformatting the staff list to a nice JSON object:
    \begin{verbatim}                                staff = [
Darden,Marcus                      {"first": "Marcus", "last": "Darden"},
Chojnacki,Alex                     {"first": "Alex", "last": "Chojnacki"},
Terwilliger,Matt                   {"first": "Matt", "last": "Terwilliger"},
Gagnon,Cameron                     {"first": "Cameron", "last": "Gagnon"},
Shah,Ankit                         {"first": "Ankit", "last": "Shah"},
                                ]\end{verbatim}
    Editors support the record and replay of \emph{macros}. With macros, you
    can start recording, puzzle out how to turn one line into the other, and
    then simply replay it for the rest. As a general rule, do not bother
    trying to be optimal or efficient, just find anything that works.
    Try starting with the column on the left and devising a macro to turn it
    into the column on the right.\\
    \textbf{Describe how to record and replay a macro.}
    \emph{\small (you do not need to include the contents of your macro)}
    \vspace{6em}
    % Easter egg for those who look, here is mine (in vim):
    % yypws^M^[i{"first": ^[A,^[kddpkJli"last": ^[A}^[0f:lli"^[wwi"^[f:lli"^[$i"^[kJ0j

\newpage
  \item Similar to how \texttt{$\sim$/.bashrc} configures your shell, a
    \texttt{$\sim$/.vimrc} or \texttt{$\sim$/.emacs} file\footnote{
      These files do not exist by default, you have to create them.
    } can configure how your editor behaves. Here are some excerpts from the
    staff's configuration files:
    \begin{lstlisting}
    .vimrc:
    set number    " double-quote means comment in vimscript; this turns on line numbers
    map ; :       " this line and the next makes ; act like : so that you don't have to
    noremap ;; ;  " hit shift all the time, typing ";;" will act as ";" used to

    .emacs:
    ; line numbers - in Emacs, ; means a comment
    (global-linum-mode t)
    (setq linum-format "%d ")
    ; Changes all yes/no questions to y/n type
    (fset 'yes-or-no-p 'y-or-n-p)
    \end{lstlisting}
    \textbf{Add something useful not listed above to your editor's configuration file.\\
      Describe  what you added and why.}
    \vspace{12em}
  \item Some final little things
    \small
    \begin{enumerate}
      \item Editors understand balanced ()'s and \{\}'s.
        \textbf{Describe how to jump from one token to its match, such as from
          the opening \{ on line~29 of \texttt{KatsBadcode} to its partner \}
          on line~58.
        }
        \vspace{4em}
      \item Now imagine if you are editing code and you determine you can
        remove an if block, for example removing the \texttt{if} on line~28 of
        \texttt{KatsBadcode} and running its body unconditionally. You need to
        fix the indentation level of all 20~lines of the body.\\
        \textbf{Describe how to change the indentation level of a block of code.}
        \vspace{4em}
      \item Sometimes it's useful to run quick little commands. For example,
        your code needs to read from a file, but you can't remember if it's
        called \texttt{sample\_data.txt} or \texttt{sampleData.txt}.\\
        \textbf{Describe how to run `ls' directly from within your editor.}
        \vspace{4em}
    \end{enumerate}
\end{enumerate}


\newpage
\section{Remote work}
One thing that can make life very convienent is learning how to work on remote
machines. CAEN has a large number of machines available for students to use
remotely, at \url{login.engin.umich.edu}. Let's check that out.

\texttt{ssh} is the \textbf{s}ecure \textbf{sh}ell program, and is used to
securely log in to remote machines.

Run \texttt{ssh login.engin.umich.edu} to log into a CAEN machine. Take a look
around, this is the same login environment and home directory as if you had
sat down at a physical CAEN machine.

Use \texttt{vim} or \texttt{emacs} to create a file called \texttt{test.txt}
on CAEN. Put some text in it, save, and quit.

Now try to run \texttt{gedit~test.txt}.

\textbf{What error do you get? Why?}
\vspace{6em}

Close your ssh session (log out of the terminal, either by typing
\texttt{exit} or pressing \texttt{Ctrl-d} at an empty prompt). Then log in
again with the additional \texttt{-X} flag to ssh:
\texttt{ssh~-X~login.engin.umich.edu}.

Now try running \texttt{gedit test.txt} -- great! Only, now you cannot do
anything else in that terminal.

\textbf{How can you keep using this terminal without killing the gedit session
  that is already running?}

\textbf{How should you launch \texttt{gedit} so that you can still use the
  terminal?}

\emph{\small (Hint: remember we talked about shell \ul{job control} a few
  weeks ago)}
\vspace{6em}

Try running a more graphically intensive program, such as the \texttt{eclipse}
IDE or \texttt{matlab}. How does it compare to sitting at a physical CAEN
machine? How does it compare to using
\href{http://caenfaq.engin.umich.edu/12374-Linux-Login-Service/how-do-i-connect-to-a-caen-linux-computer-remotely}{VNC}
to log into CAEN? (And how good is your Internet connection right now ;) ?)

\bigskip
\hrule
You may also find the \textbf{s}ecure \textbf{c}o\textbf{p}y program,
\texttt{scp}, useful for moving files between your machine and the remote
machine. Assuming you have the file `test.txt' on your local machine,

\texttt{scp~test.txt~login.engin.umich.edu:}

will copy the file to CAEN. Note the trailing colon, this is what tells
\texttt{scp} to copy to a remote machine.

You can also specify a path on one or both machines. Assuming that you have
the folder `inhomeoncaen' on your CAEN account and `local' in the current
directory of your machine,

\texttt{scp~login.engin.umich.edu:inhomeoncaen/test.txt~local/}

will the file \texttt{test.txt} from CAEN to your machine.

\texttt{scp} operates just like \texttt{cp}, that is, you have to pass the
\texttt{-r} flag if you want to copy a directory, such as

\texttt{scp~-r~project1~login.engin.umich.edu:classes/eecs280/}

\emph{(There's no question on \texttt{scp}, just a tool for you to play with)}

\end{document}
